---
title: "Iteration and List Columns"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


Load key packages

```{r}
library(tidyverse)
library(rvest)
```


## Here's some lists

```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
  )

l

l$mat

l[["mat"]][1, 3] #access list of matrix "mat", row 1, col 3

l[[1]]
l[[4]]
```


Make a list that's hopefully a bit more useful.

To transmit typing across multiple lines --> on Mac shift+option + highlight multiple lines + type
```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```


Let's reuse the function we wrote last time.

```{r}
mean_and_sd = function(x) {
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
  
}
```

Let's use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

## Use a for loop

Create output list, and run a for loop

```{r}
output = vector("list", length = 4) #creating an empty list with four spots

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output

```


## Do the ame thing

but with `map` instead

```{r}
output = map(list_norm, mean_and_sd)
```


let's do a couple of other things

```{r}
output = map(list_norm, median)

output = map_dbl(list_norm, IQR) #dbl simplifies the output from a list to something easier to see

output = map_dfr(list_norm, mean_and_sd) #map into dataframne


output = 
  map(list_norm, mean_and_sd) |> 
  bind_rows()
```


## List Columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"), #need to have same # of things in name column and ilst_norm columns
    samp = list_norm
  )

listcol_df #output shows that there are 20 numbers in each row

listcol_df |> 
  filter(name %in% c("a", "b")) #just get the first 2 rows


listcol_df |> 
  select(-samp)
```

```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])
mean_and_sd(listcol_df[["samp"]][["b"]])

#use map to do the same thing
map(listcol_df[["samp"]], mean_and_sd) #mapping across samp column that was extracted from listcol_df and calculate mean_and_sd

#Difference between map and map_dbl
  #map by default always returns a list
  #map_dbl makes the list of numbers into vectors (simplified)

```

Add a list column

```{r}
listcol_df |> 
  mutate(output = map(samp, mean_and_sd)) #samp is a column in the dataframe (no need to extract), so map across column samp, and compute mean and sd and add a new column 

listcol_df |> 
  mutate(output = map(samp, mean_and_sd),
  iqr = map_dbl(samp, IQR))

listcol_df |> 
  mutate(output = map(samp, mean_and_sd),
  iqr = map_dbl(samp, IQR)) |> 
  select(-samp) |> 
  unnest(output) #similar to bindrows fx to df -- taking a nested  df and expanding it

```

### NSDUH 

```{r}
nsduh_table_format = function(html, table_num) {
  
  out_table =
    html |> 
    html_table() |> 
    nth(table_num) |> 
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(out_table)
  
}
```

We need to import the html, and then extract the correct tables.

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```


```{r}
nsduh_table_format(html = nsduh_html, table_num = 1)
nsduh_table_format(html = nsduh_html, table_num = 4)
nsduh_table_format(html = nsduh_html, table_num = 5)
```


Learning Assessment
Make a table with drug names, table number, and column with the associated tables
```{r}
nsduh_df =
  tibble(
    drug = c("marijuana", "cocaine", "heroin"),
    table_n = c(1, 4, 5)
  ) |> 
  mutate(table = map(table_n, nsduh_table_format, html = nsduh_html)) |> 
  unnest(table)


```

