---
title: "Iteration and List Columns"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


Load key packages

```{r}
library(tidyverse)
library(rvest)
```


## Here's some lists

```{r}
l = list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
  )

l

l$mat

l[["mat"]][1, 3] #access list of matrix "mat", row 1, col 3

l[[1]]
l[[4]]
```


Make a list that's hopefully a bit more useful.

To transmit typing across multiple lines --> on Mac shift+option + highlight multiple lines + type
```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```


Let's reuse the function we wrote last time.

```{r}
mean_and_sd = function(x) {
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  out_df = 
    tibble(
      mean = mean_x,
      sd = sd_x
    )
  
  return(out_df)
  
}
```

Let's use the function to take mean and sd of all samples.

```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

## Use a for loop

Create output list, and run a for loop

```{r}
output = vector("list", length = 4) #creating an empty list with four spots

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}

output

```


## Do the ame thing

but with `map` instead

```{r}
output = map(list_norm, mean_and_sd)
```


let's do a couple of other things

```{r}
output = map(list_norm, median)

output = map_dbl(list_norm, IQR) #dbl simplifies the output from a list to something easier to see

output = map_dfr(list_norm, mean_and_sd) #map into dataframne


output = 
  map(list_norm, mean_and_sd) |> 
  bind_rows()
```


## List Columns


